Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaEvolution.tex
Ongoing: address Alexei's comments

We developed and deployed a single-point solution to better understand the
problem space and study abstractions for the integration of HTC and HPC
computing paradigms. Specifically, the PanDA team developed a job broker to
support the execution of part of the ATLAS production Monte Carlo workflow on
Titan, a leadership-class supercomputer managed by the Oak Ridge Leadership
Computing Facility (OLCF) at the Oak Ridge National Laboratory (ORNL).

@@

>>>>

We developed and deployed a single-point solution to better understand the
problem space of enabling a WMS designed for HTC to execute production workflows
on resources designed to support HPC. The PanDA team developed a job broker to
support the execution of part of the ATLAS production Monte Carlo workflow on
Titan, a leadership-class supercomputer managed by the Oak Ridge Leadership
Computing Facility (OLCF) at the Oak Ridge National Laboratory (ORNL).

@@

\mtnote{Address Alexei's comments: Add a paragraph explaining how this solution has been ported to other HPC machines and reference relevant publications.}
